---
title: "Explanation of Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explanation of Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753KESKEWFA23)
```

## Introduction

This is a package comprised of functions and data  for MATH4753 in the Fall 2023 semester. This package represents a small selection of functions and data used throughout the term, generally chosen for inclusion at the discretion of the creator.

# Fire - Data

This is the data set used in Project 2. It relates the distance from a fire station to the damage caused by a residential fire. It is a small set of data helpful for learning linear regression.

# mybin

mybin() creates barplot from a binomial simulation for a given number of iterations and trials. The probability of success in each trial must also be specified.

```{r}
mybin(100,10,.5)
```

# myci

myci() creates a 95% confidence interval using qt() and a specified set of data.

```{r}
myci(rnorm(30,mean=10,sd=12))
```

# myclt

myclt() takes input information on a sample and then a specified lower and upper bounds with defaults of 0 and 5, respectively, to create a histogram of the sum of samples.

```{r}
myclt(10,1000)
```

# myncurve

myncurve() requires a mean and standard deviation as well as an upper bound as inputs. In turn, it produces a normal curve and calculates and shades in the probability of a value being between 0 and the specified upper bound.

```{r}
myncurve(10,5,6)
```

#ntickets

This function was created for project 1's airline overbooking problem. Accepting arguments regarding the seats on the aircraft, desired probability of overbooking, and the probability that a ticketed passenger boards, it finds the optimal number of tickets to sell.

```{r}
ntickets(200,.02,.95)
```
